---
title: Game Play Analytics
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQNfffI7pW3SpAGlO3bBGx6RQBoG4CL9OrQ7sChMHXvrgWci22OVJ4MPqxwPWAexEj4PD3XyQ76WA9N/pub?output=csv")
latest_data <- logged_data %>%
  rename(
    game = "Do you play Game?",
    play_time = "How many hours do you usually play games per week?",
    platform = "On what platform do you usually play games?"
  )

summary(latest_data$play_time)
mean_play_time <- mean(latest_data$play_time, na.rm = TRUE)
median_play_time <- median(latest_data$play_time, na.rm = TRUE)

game_counts <- latest_data %>% 
  count(game) %>% 
  mutate(percentage = n / sum(n) * 100)

platform_split <- latest_data %>%
  separate_rows(platform, sep = ",") %>%
  mutate(platform = str_trim(platform)) %>%
  filter(platform != "")

platform_counts <- platform_split %>% 
  count(platform) %>% 
  mutate(percentage = n / nrow(latest_data) * 100)

ggplot(platform_counts, aes(x = reorder(platform, -n), y = n)) +
  geom_col(fill = "blue") +
  labs(
    title = "platform distribution",
    x = "platform",
    y = "number_of_ppl"
  ) +
  theme_minimal()

play_time_categories <- latest_data %>%
  mutate(play_time_group = case_when(
    play_time < 10 ~ "less than 10 hour",
    play_time >= 10 & play_time <= 30 ~ "10 to 30 hours",
    play_time > 30 ~ "more than 30 hours"
  )) %>%
  count(play_time_group) %>%
  mutate(percentage = n / sum(n) * 100)


```

```{css}
body {
  font-family: Arial, sans-serif;
  line-height: 1.6;
  color: #333;
}
h2 {
  color: #2c3e50;
  border-bottom: 2px solid #3498db;
  padding-bottom: 5px;
}
```


```{r}
ggplot(play_time_categories, aes(x = factor(play_time_group, 
                                            levels = c("less than 10 hour", 
                                                       "10 to 30 hours", 
                                                       "more than 30 hours")), 
                                 y = n)) +
  geom_col(fill = "orange") +
  labs(
    title = "Weekly Play Time Distribution",
    x = "Play Time",
    y = "number_of_ppl"
  ) +
  theme_minimal()
```

The average play time is `r round(mean_play_time, 1)` hours per week, with a median of `r round(median_play_time, 1)` hours.

`r play_time_categories$play_time_group[which.max(play_time_categories$n)]` is the most common play duration category, representing `r round(play_time_categories$percentage[which.max(play_time_categories$n)], 1)`% of people.



```{r}
ggplot(platform_counts, aes(x = reorder(platform, -n), y = n)) +
  geom_col(fill = "blue") +
  labs(
    title = "platform distribution",
    x = "platform",
    y = "number_of_ppl"
  ) +
  theme_minimal()
```

`r platform_counts$platform[which.max(platform_counts$n)]` is the most popular platform, with `r round(platform_counts$percentage[which.max(platform_counts$n)], 1)`% of people using it.

